
\documentclass[12pt,a4paper]{report}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{tocloft}
\usepackage{hyperref}

\geometry{left=1.5in, right=1in, top=1in, bottom=1in}
\titleformat{\chapter}[display]
  {\normalfont\huge\bfseries}{\chaptername\ \thechapter}{20pt}{\Huge}
\onehalfspacing

\begin{document}

% Title Page
\begin{titlepage}
\centering
{\Large \textbf{Maharshi Dayanand University}}\\[1cm]
{\Large Department of Computer Science and Engineering}\\[2cm]
{\Huge \textbf{AI-Powered Energy Efficiency and Climate-Responsive Forecasting System}}\\[2cm]
{\Large Submitted by: \textbf{Ishita Bahamnia}}\\[0.5cm]
{\Large Supervisor: \textbf{Dr. Yogesh Kumar}}\\[4cm]
{\large Thesis submitted in partial fulfillment for the award of the degree of}\\[0.5cm]
{\Large \textbf{Master of Technology (M.Tech) in Computer Science}}\\[3cm]
{\Large \textbf{June 2025}}\\
\end{titlepage}

% Declaration
\chapter*{Declaration}
I hereby declare that the thesis titled “AI-Powered Energy Efficiency and Climate-Responsive Forecasting System” submitted to Maharshi Dayanand University is an original work carried out by me under the guidance of Dr. Yogesh Kumar and has not been submitted elsewhere for the award of any other degree.

\vspace{1cm}
\begin{flushright}
\textbf{Ishita Bahamnia}\\
Roll No.: [Your Roll Number]
\end{flushright}

% Acknowledgment
\chapter*{Acknowledgment}
I would like to express my sincere gratitude to my supervisor, Dr. Yogesh Kumar, for his invaluable support, guidance, and encouragement throughout the course of this work. I am also thankful to Maharshi Dayanand University for providing the resources and environment conducive to research.

% Abstract
\chapter*{Abstract}
This thesis proposes a Multi-Agent System (MAS) empowered by AI for improving energy efficiency in smart grids through reinforcement learning, optimization, and anomaly detection. Utilizing datasets from CEA, MNRE, and IMD, the system integrates LSTM, Pyomo, and Isolation Forest models to simulate and evaluate real-time decision-making. Results demonstrate a 15\% improvement in energy efficiency, reduced losses, and enhanced renewable integration. The model supports ISO 50001 standards and aligns with SDG 7.

% Table of Contents and Lists
\tableofcontents
\listoffigures
\listoftables

\chapter{Chapter 1}
\input{chapter1.tex}
\chapter{Chapter 2}
\input{chapter2.tex}
\chapter{Chapter 3}
\input{chapter3.tex}
\chapter{Chapter 4}
\input{chapter4.tex}
\chapter{Chapter 5}
\input{chapter5.tex}
\chapter{Chapter 6}
\input{chapter6.tex}
\chapter{Chapter 7}
\input{chapter7.tex}
\chapter{Chapter 8}
\input{chapter8.tex}

% References
\chapter*{References}
\addcontentsline{toc}{chapter}{References}
[1] Hochreiter, S., & Schmidhuber, J. (1997). Long short-term memory. Neural computation, 9(8), 1735-1780.\\
[2] POSOCO, MNRE, and IMD portals.\\
[3] ISO 50001 Standard Guidelines.\\
[4] IEEE Smart Grid Whitepapers.\\

\end{document}
